%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

% \documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\documentclass[margin]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{hyperref}
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

% Makes the random asterisk (*), that appears above the bibtex references for some reason, disappear.
% See http://tex.stackexchange.com/questions/28339/random-asterisk-when-using-bibtex-and-res-cls
\makeatletter
\renewenvironment{thebibliography}[1]
     {\list{\@biblabel{\@arabic\c@enumiv}}%
           {\settowidth\labelwidth{\@biblabel{#1}}%
            \leftmargin\labelwidth
            \advance\leftmargin\labelsep
            \@openbib@code
            \usecounter{enumiv}%
            \let\p@enumiv\@empty
            \renewcommand\theenumiv{\@arabic\c@enumiv}}%
      \sloppy
      \clubpenalty4000
      \@clubpenalty \clubpenalty
      \widowpenalty4000%
      \sfcode`\.\@m}
     {\def\@noitemerr
       {\@latex@warning{Empty `thebibliography' environment}}%
      \endlist}
\makeatother
\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Alexej Gossmann} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{Department of Mathematics} % Your address
\moveleft.5\hoffset\centerline{Tulane University} % Your address
\moveleft.5\hoffset\centerline{6823 St.Charles Ave.} % Your address
%\moveleft.5\hoffset\centerline{Office: Gibson 313A} % Your address
\moveleft.5\hoffset\centerline{New Orleans, LA 70118}

\vspace{5pt}
\moveleft.5\hoffset\centerline{\textbf{Web:} \href{http://www.alexejgossmann.com/}{alexejgossmann.com}} 
\moveleft.5\hoffset\centerline{\textbf{Email:} \href{mailto:agossman@tulane.edu}{agossman@tulane.edu}}

\vspace{5pt}
\moveleft.5\hoffset\centerline{Updated: \today} 

%----------------------------------------------------------------------------------------

\begin{resume}
%
%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
%
%\section{OBJECTIVE}  
%
%A position in the field of computers with special interests in business applications programming, information processing, and management systems. 
%
%----------------------------------------------------------------------------------------
%	AREAS OF SPECIALIZATION
%----------------------------------------------------------------------------------------

\section{AREAS OF INTEREST}

Statistical learning with sparsity, mixed effects models, genomics and brain imaging data analysis

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl PhD,} Mathematics \\
Tulane University, New Orleans, Louisiana, expected May 2018

{\sl MS,} Statistics \\
Tulane University, New Orleans, Louisiana, May 2014\\
Master's Research Project: Analysis of Bone Growth Data with Mixed-Effects SS ANOVA Methods (supervised by Dr. Michelle Lacey)\\
GPA: 3.975

{\sl BS,} Mathematics\\
Technische Universit\"{a}t Darmstadt, Darmstadt, Germany, May 2012\\
Thesis: On disjunction and numerical existence properties of extensions of Heyting arithmetic (supervised by Dr. Ulrich Kohlenbach)\\
GPA: 4.0

{\sl Summer Schools and Workshops} 
\begin{itemize}
\item {\it SAMSI Distributed and Parallel Data Analysis Workshop}, North Carolina State University. September 2016.
\item {\it SAMSI Optimization Opening Workshop}, Hamner Conference Center in Research Triangle Park, NC. August 2016.
\item {\it SAMSI Optimization Summer School}, Hamner Conference Center in Research Triangle Park, NC. August 2016.
\item {\it 2nd Summer Institute in Statistics for Big Data}. University of Washington. July 2016.
  Modules attended: Big Data Wrangling with R, Visualization of Biomedical Big Data.
\item {\it 21st Summer Institute in Statistical Genetics}. University of Washington School of Public Health. July 2016.
  Modules attended: Quantitative Genetics.
\item {\it 20th Summer Institute in Statistical Genetics}. University of Washington School of Public Health. July 2015.
  Modules attended: Unsupervised Methods for Statistical Machine Learning, MCMC for Genetics, Pathway \& Network Analysis for Omics Data
\item {\it SAMSI 2014 Mathematical and Statistical Modeling Workshop for Graduate Students}, North Carolina State University. July 2014.
  Project: Allergy, Asthma and Exposures in the Homes of the US Population (supervised by scientists from Rho Inc.).
\end{itemize} 
 
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Teaching Experience}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item \emph{Instructor}: Calculus 1, Tulane University, Department of Mathematics, Fall 2014.
\item \emph{Co-Teacher}: Statistics for Scientists, Tulane University, Department of Mathematics, Spring 2014.
\item \emph{Teaching Assistant}: Various Statistics, Calculus, and Real Analysis courses at Tulane University and Technische Universit\"{a}t Darmstadt, Fall 2010 - Spring 2014.
%\item \emph{Teaching Assistant}: Statistics for Business (Fall 2012 and Spring 2013), Statistics for Scientists (Fall 2012), Probability and Statistics (Fall 2013), Calculus 1 (Fall 2013), Real Analysis (Spring 2014), Analysis 1 (Fall 2010) and Analysis 2 (Spring 2011).
\end{itemize}

{\sl Internships} 
\begin{itemize}
\item {\it Student developer for Google Summer of Code 2015}. Project: Adding Linear Mixed Effects Models Support to SciRuby. Supervised by the Ruby Science Foundation. May -- August 2015.
\end{itemize} 

{\sl Professional Service Activities}
\begin{itemize}
\item {\it Mentor for Google Summer of Code 2016}. Project: Categorical data support for Daru, Statsample and Statsample-glm. May -- August 2016.
\item President of the SIAM student chapter at Tulane University. September 2014 -- September 2016.
\item Main organizer of the Graduate Student Colloquium at the department of Mathematics, Tulane University. September 2014 -- September 2016.
\end{itemize}

{\sl Other}
\begin{itemize}
\item Kommando 1. Luftwaffendivision, F\"{u}rstenfeldbruck. Military service at the department for public relations and press. June 2008 -- February 2009.
\end{itemize} 

\section{PUBLICATIONS}

\bibliographystyle{unsrt} %keep list of references unsorted (i.e. sort manualy in the bib file)
\bibliography{cv}
\nocite{*}

%\begin{itemize} \itemsep -2pt % Reduce space between items
%    \item A. Gossmann, S. Cao, and Y.-P. Wang. {\it Identification of Significant Genetic Variants via SLOPE, and its Extension to Group SLOPE.} In Proceedings of the International Conference on Bioinformatics, Computational Biology and Biomedical Informatics, BCB’15, New York, NY, USA, 2015. ACM.
%    \item S. Cao, H. Qin, A. Gossmann, H.-W. Deng, and Y.-P. Wang. {\it Unified Tests for Fine Scale Mapping and Identifying Sparse High-Dimensional Sequence Associations.} In Proceedings of the International Conference on Bioinformatics, Computational Biology and Biomedical Informatics, BCB’15, New York, NY, USA, 2015. ACM.
%\end{itemize}

\section{TALKS AND COLLOQUIA}

\begin{itemize} \itemsep -2pt % Reduce space between items
    \item Title: {\it Understanding Probabilistic Numerics}. Graduate student colloquium, Tulane University, September 2016.
    \item Title: {\it A sparse regression method for group-wise feature selection with false discovery rate control}. Graduate student colloquium, Tulane University, 2016.
    \item Title: {\it Identification of Significant Genetic Variants via SLOPE, and its Extension to Group SLOPE}. The 6th ACM Conference on Bioinformatics, Computational Biology, and Health Informatics, Atlanta, GA, September 2015.
    \item Title: {\it Reproducing Kernel Hilbert Spaces and Smoothing Spline Regression}. Graduate student colloquium, Tulane University, March 2014.
\end{itemize}

\section{POSTER PRESENTATIONS}

\begin{itemize} \itemsep -2pt % Reduce space between items
    \item A. Gossmann and Y.P. Wang, SlopeCCA and gslopeCCA: sorted L1 penalized canonical correlation analysis (Abstract/Program \#2803W). Presented at the 66th Annual Meeting of The American Society of Human Genetics, October 19, 2016, Vancouver, Canada.
    \item A. Gossmann, S. Cao, and Y.-P. Wang, Identification of Significant Genetic Variants via SLOPE, and its Extension to Group SLOPE (Abstract/Program \#1343F). Presented at the 65th Annual Meeting of The American Society of Human Genetics, October 9, 2015, Baltimore, MD.
\end{itemize}

\section{SOFTWARE}

\begin{itemize} \itemsep -2pt % Reduce space between items
    \item \verb!grpSLOPE! -- Group SLOPE (Group Sorted L1 Penalized Estimation) is a penalized linear regression method that is used for adaptive selection of groups of significant predictors in a high-dimensional linear model. The Group SLOPE method can control the (group) false discovery rate at a user-specified level. Project repository: \url{https://github.com/agisga/grpSLOPE}. CRAN: \url{https://cran.r-project.org/web/packages/grpSLOPE/index.html} 
    \item \verb!mixed_models! -- Fit statistical linear models with fixed and random effects in Ruby. Project repository: \url{https://github.com/agisga/mixed_models}. RubyGems: \url{https://rubygems.org/gems/mixed_models}.
    \item \verb!spitzy! -- A toolbox of numerical differential equation solvers written in pure Ruby. Project repository: \url{https://github.com/agisga/spitzy}. RubyGems: \url{https://rubygems.org/gems/spitzy}.
    \item I am an active code contributor to projects of the Ruby Science Foundation (SciRuby), such as \verb!NMatrix! (\url{https://github.com/SciRuby/nmatrix}), \verb!statsample-glm! (\url{https://github.com/SciRuby/statsample-glm}), and others.
\end{itemize}
 
%----------------------------------------------------------------------------------------
%	(COMPUTER) SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{SKILLS} 

{\sl Computer skills:}
R, Ruby, C++, Matlab, \LaTeX, Linux, git and github, HTML, CSS.

{\sl Language Knowledge:}
Bilingual in German and Russian, fluent in English, basic knowledge of French.

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------
%
%\section{EXTRA-CURRICULAR \\ ACTIVITIES} 
%
%Elected {\it House Manager}, Rho Phi Sorority \\
%Elected {\it Sports Chairman} \\
%Attended Krannet Leadership Conference \\
%Headed delegation to Rho Phi Congress \\
%Junior varsity basketball team \\
%Participant, seven intramural athletic teams 

%----------------------------------------------------------------------------------------

\end{resume}

\end{document}
